Relationship between solar wind, $D_{st}$, and plasmasphere trough mass density on one-hour time scales

### 2015-12-08 paper.tex
Adding random event plot to paper
paper edits

\begin{document}
\title{Relationship between solar wind, $D_{st}$, and plasmasphere mass density on one-hour time scales}
\author{
Victoir Veibell\footnote{vveibell@gmu.edu}
\and
R.S. Weigel\footnote{rweigel@gmu.edu}}

@@

\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period and 1991 and found that the average ion mass density, $M=\rho/n_e$, correlated with geomagnetic activity, with lower $D_{st}$ values corresponding to slightly average ion mass densities.  They also found a relationship between the average ion mass and 1.5- and 3-day averages of $K_p$ were compared to $M$.  Most measurements occurred in the MLT range of 12:00 and 18:00 in the plasma trough, and CRRES had a nearly equatorial orbit.

\cite{Takahashi2010} developed a mass density dataset using measurements from the GOES satellites over the years 1980 through 1992, with most measurements in the range $L=6.8\pm0.2$. The equatorial mass density, $\rho_{eq}$ was estimated from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}L/(R/R_E)$. The mass density $\rho$ was estimated using the the Alfven wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of an infinitely conducting ionosphere.

@@

The results of \cite{Takahashi2006} and \cite{Takahashi2010} are consistent with other results on changes in mass density in the plasma trough region.  \cite{Yao2008} studied the relationship between $D_{st}$ and ion number density for different ions in different regions (ring current and plasma sheet) and found a general correlation during each of the four storms considered.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/alldata.eps}
\caption{Overview of data used in this study. The top four panels show parameters from \cite{Reconstruction} and the bottom panel is based on $\rho_{eq}$ from \cite{Denton} after interpolation and averaging described in the text. Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st}=-50$~nT and $\rho_{eq}=40$~amu/cm$^3$}.
\label{AllData}
\end{figure}

@@

\begin{figure}[htp!]
\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-sat6.eps}
\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-sat7.eps}
\caption{GOES Satellite 6 and 7}
\end{figure}

\begin{figure}[htp!]
\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-sat2.eps}
\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-sat5.eps}
\caption{GOES Satellite 2 and 5}
\end{figure}
\clearpage

\begin{figure}[htp!]
\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-tak.eps}
\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-detrend.eps}
\caption{Top: From 89-91. Bottom: With $\rho_{eq}$ LT medians subtracted}
\end{figure}

\begin{figure}[htp!]
\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst80.eps}
\includegraphics[scale=0.45]{paperfigures/AEbyhour.eps}
\caption{Top: $D_{st}<-80$~nT. Bottom: $AE$ events by their hour of onset}
\end{figure}

>>>>

\begin{document}
\title{Relationship between solar wind, $D_{st}$, and plasmasphere trough mass density on one-hour time scales}
\author{
Victoir Veibell\footnote{vveibell@gmu.edu}
\and
R.S. Weigel\footnote{rweigel@gmu.edu}}

@@

\cite{Takahashi2006} estimated magnetospheric mass density using measurements from the CRRES satellite during a 73-day period and 1991 and found that the average ion mass density, $M=\rho/n_e$, correlated with geomagnetic activity, with lower $D_{st}$ values corresponding to slightly higher average ion mass densities.  They also found a relationship between the average ion mass and 1.5- and 3-day averages of $K_p$ were compared to $M$.  Most measurements occurred in the MLT range of 12:00 and 18:00 in the plasma trough, and CRRES had a nearly equatorial orbit.

\cite{Takahashi2010} developed a mass density dataset using measurements from the GOES satellites over the years 1980 through 1992, with most measurements in the range $L=6.8\pm0.2$. The mass density $\rho$ was estimated using the the Alfven wave velocity relationship, $V_A=B/\sqrt{\mu_0\rho}$, a magnetic field model, and a numerical solution to a wave equation with an ionospheric boundary and the assumption of a zero resistance ionosphere.  The equatorial mass density, $\rho_{eq}$, was estimated from the estimated mass density using a power law dependence on the geocentric distance to the field line of the observation, $R$, $\rho=\rho_{eq}L/(R/R_E)$.

@@

The results of \cite{Takahashi2006} and \cite{Takahashi2010} are consistent with other results on changes in mass density in the plasma trough region.  \cite{Yao2008} studied the relationship between $D_{st}$ and ion number density for different ion species in different regions (ring current and plasma sheet) and found a general correlation during each of the four storms considered.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/alldata-GOES6-1983-1991.eps}
\caption{Overview of data used in this study. The top four panels show parameters from \cite{Reconstruction} and the bottom panel is based on $\rho_{eq}$ from \cite{Denton} after interpolation and averaging described in the text. Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st}=-50$~nT and $\rho_{eq}=40$~amu/cm$^3$}.
\label{AllData}
\end{figure}

@@

\begin{figure}[htp!]
\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1983-1991.eps}
\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES7-1987-1991.eps}
\caption{GOES Satellite 6 and 7}
\end{figure}

\begin{figure}[htp!]
\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES2-1981-1983.eps}
\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES5-1983-1987.eps}
\caption{GOES Satellite 2 and 5}
\end{figure}
\clearpage

\begin{figure}[htp!]
\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1989-1991.eps}
\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst80.eps}
\caption{Top: From 89-91 (compare to Takahashi 2010). Bottom:  $D_{st}<-80$~nT.}
\end{figure}

\begin{figure}[htp!]
\includegraphics[scale=0.45]{paperfigures/AEbyhour.eps}
\caption{$AE$ events by their hour of onset}
\end{figure}
\clearpage

\begin{figure}[htp!]
\includegraphics[scale=0.45]{paperfigures/DstRhoThresh-1983-1991.eps}
\includegraphics[scale=0.45]{paperfigures/DstRhoThresh-1987-1991.eps}
\caption{High $F_{10.7}$ events - Low $F_{10.7}$ events, both with baselines removed. 83-91 and 87-91}
\end{figure}

\begin{figure}[htp!]
\includegraphics[scale=0.45]{paperfigures/DstRhoThresh-1983-1987.eps}
\includegraphics[scale=0.45]{paperfigures/DstRhoThresh-1981-1983.eps}
\includegraphics[scale=0.45]{paperfigures/RandRhoThresh-1983-1991.eps}
\caption{High $F_{10.7}$ events - Low $F_{10.7}$ events, both with baselines removed. 83-87 and 81-83. Bottom: Random "events" from 1983-1991}
\end{figure}
\clearpage

\begin{figure}[htp!]
\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1983-1991.eps}
\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES7-1987-1991.eps}
\caption{Comparing GOES 6 to GOES 7}
\end{figure}

\begin{figure}[htp!]
\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1983-1987.eps}
\includegraphics[scale=0.45]{paperfigures/HighLowF107rhoeq-Dst50-GOES6-1987-1991.eps}
\caption{GOES 6 from 83-87 and 87-91}
\end{figure}
